Proportional multi-state multiple-cohort life table model

### 2018-04-20 MSLT/MSLTdoc.Rmd
Remove pop_five_year from input_life_table dataframe and then join it GBD_population_gl to get pop_five_year

##Create empty data frame
input_life_table <- as.data.frame(matrix(0, ncol=5, nrow = 202))
##Give variables names (mx=total mortality rate, yldsx = total years lived with disability rates )
names(input_life_table) <- c("age", "sex", "pop_five_year", "mx", "yldsx")
##Populate life table: Age, 0 to 100
input_life_table[1:101, 1] <- c(0:100)
input_life_table[102:202, 1] <- c(0:100)
##Populate life table: sex, male, female
input_life_table[1:101, 2] <- "male"
input_life_table[102:202, 2] <- "female"
##Create variable age_sex to match with population data. 
input_life_table$sex_age_cat <- paste(input_life_table$sex,input_life_table$age, sep = "_"  )

##Populate life table: five_year_pop. SEE LIFE TABLE LOOPS THAT USES 5 YEAR POP. 
input_life_table$pop_five_year <- if(
  input_life_table$sex_age_cat == GBD_population_GL$pop_five_year, GBD_population_GL$pop_five_year, NA)

>>>>

##Create empty data frame
input_life_table <- as.data.frame(matrix(0, ncol=4, nrow = 202))
##Give variables names (mx=total mortality rate, yldsx = total years lived with disability rates )
names(input_life_table) <- c("age", "sex", "mx", "yldsx")
##Populate life table: Age, 0 to 100
input_life_table[1:101, 1] <- c(0:100)
input_life_table[102:202, 1] <- c(0:100)
##Populate life table: sex, male, female
input_life_table[1:101, 2] <- "male"
input_life_table[102:202, 2] <- "female"
##Create variable age_sex to match with population data. 
input_life_table$sex_age_cat <- paste(input_life_table$sex,input_life_table$age, sep = "_"  )

##Populate life table: five_year_pop. SEE LIFE TABLE LOOPS THAT USES 5 YEAR POP.

input_life_table <- merge(input_life_table, select(GBD_population_GL
                                                     ,c(sex_age_cat, pop_five_year))
                                                     , by = 'sex_age_cat', all.x = TRUE)

#input_life_table$pop_five_year <- ifelse(
#  input_life_table$sex_age_cat == GBD_population_GL$pop_five_year, #GBD_population_GL$pop_five_year, NA)
